---
title: "Project proposal"
author: "INFINITE"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

The dataset "USvideos" came from the Kaggle website and was collected by YouTube API, the dataset includes several months of data on the daily trending US YouTube videos. To determine the year’s top-trending videos, YouTube uses a combination of factors including measuring users interactions(number of views, comments, and likes). 

The general research theme is “To find the most popular type of video, through considering following three factors: number of views, comments, and likes. 

The variables that we will mainly use would be:
title, channel_title, category_id, tags, and description-- these variables help us to determine type of the most popular video, from multiple angles;
views, likes, comment_count-- these three variables indicate the popularity of each video.


## 2. Data
```{r}
USvideos <- read_csv("../data/USvideos.csv")
glimpse(USvideos)
```


## 3. Data analysis plan

The outcome variables will be number of views, comments, and likes; and predictor variables will be video_id, category_id, and publish_time.

We plan to make comparisons on different categories, to research which category generally is the most popular one.

We are planning on using a ridge plot or histogram to visualize the data as this fulfills our plan to use fill. 

We are also planning on using basic summary statistics such as median, minimum value, and maximum value. Using the summary statistics for the views, likes, and comments, will give us representative numbers of the average amount for every video category. We need statistical methods to display which type of videos is the most popular. 

Lastly, these statistics analysis should indicate a certain type of youtube video that generally receives most likes, views, and comments, as the most popular type.




