---
title: "Project proposal"
author: "INFINITE"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

The dataset "USvideos" came from the Kaggle website and was collected by YouTube API, the dataset includes several months of data on the daily trending US YouTube videos. To determine the year’s top-trending videos, YouTube uses a combination of factors including measuring users interactions(number of views, comments, and likes). 

The general research question is “Which is the most popular type of video, through considering following three factors: number of views, comments, and likes". 

The variables that we will mainly use would be:
category_id-- we will use this variable to determine type of the most popular video (to find the category in json file, according to the category_id);
views, likes, comment_count-- these three variables indicate the popularity of each video;
We will also use title, channel_title, tags, and description, to further determine type of the most popular video.


## 2. Data
```{r}
USvideos <- read_csv("../data/USvideos.csv")
glimpse(USvideos)
```


## 3. Data analysis plan

The outcome variables will be number of views, comments, and likes; and predictor variables will be category_id.

We plan to make comparisons on different categories, to research which category generally is the most popular one.

We are also planning to summarise each video category's total number of views. Besides, we weill also calculate the proportion of comments (comments/views) and the proportion of likes (likes/views). Since we believe that apart from having many viewers, a popular video should also receive high proportion of likes as well as comments （the video content should inspire viewers to discuss).

We plan to use bar plot to visualize the data, as it can directly and clearly display the comparison between different video types. 

Our exploration theme is to find out the most popular type of video, these statistics analysis should indicate a certain type of youtube video that generally receives most likes, views, and comments, as the most popular type.

We expect the video type that has highest likes and comments proportion is the same type, also it has high number of viewers.

```{r}
USvideos %>%
  count(category_id, views, likes, comment_count) %>%
  group_by(category_id) %>%
  mutate(prop_like = likes/views, prop_comment = comment_count/views) %>%
  select(prop_like, prop_comment)
```


