---
title: "Project proposal"
author: "INFINITE"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```


## 1. Introduction

The data set "USvideos" comes from the Kaggle website and was collected by YouTube API, the data set includes several months of data on the daily trending US YouTube videos. To determine the year’s top-trending videos, YouTube uses a combination of factors including measuring user interaction(number of views, comments, and likes). 

The general research question is “What is the most popular video on Youtube, factoring in the number of views, comments, and likes". 

The variables that we will mainly use would be:
category_id - We will use this variable to determine the most popular video (find the category in json file, according to the category_id);
views - This variable will indicate the number of viewers on a video,
likes - THis variable will indicate the number of likes on a video, 
comment_count - This variable will indicate the number of comments on a video,
All three of these variables will help us determine the popularity of each video. these three variables indicate the popularity of each video,
We will also use title, channel_title, tags, and description to further examine how these have an effect on how popular a video might become. 

## 2. Data
```{r}
USvideos <- read_csv("../data/USvideos.csv")
glimpse(USvideos)
```


## 3. Data analysis plan

The outcome variables will be the number of views, comments, and likes; and predictor variables will be the category_id.

We plan to compare different categories to understand which category generally is the most popular.

We are also planning to summarize each videos total number of views. Also, we we will also calculate the proportion of comments (comments/views) and the proportion of likes (likes/views). Since we believe that apart from having many viewers, a popular video should also receive a high proportion of likes as well as comments （the video content should inspire viewers to discuss).

We plan to use a bar plot to visualize the data, as it can directly and clearly coomunicate the comparison between different video types. 

Our exploration theme is to find out the most popular type of video, these statistics analysis should indicate certain types of Youtube video that receives the most likes, views, and comments as the most popular video.

We expect the video type that has the largest number of likes, comments and viewers to be the most popular on Youtube


```{r}
USvideos %>%
  count(category_id, views, likes, comment_count) %>%
  group_by(category_id) %>%
  mutate(prop_like = likes/views, prop_comment = comment_count/views) %>%
  select(prop_like, prop_comment)
```


