---
title: "Youtube"
subtitle: " "
author: "Infinite <br> Alicia, Lucas, Lucia"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, uo-fonts]
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
library(tidyverse)
library(knitr)
library(palmerpenguins)
library(tidymodels)
library(broom)
library(here)
library(dplyr)
library(stringr)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```


```{r load-data, include = FALSE}
USvideos <- read_csv(here("data/USvideos.csv"))
```


class: center, middle, inverse

# What makes a Youtube video popular?

---


class: inverse, top, middle

# Packages Used


- Tidyverse
- Knitr
- Palmerpenguins
- Tidymodels
- Broom
- Here
--

- Dplyr, Select and display accordingly
- Stringr, Filter question and exclamation marks

---
class: inverse, center, middle

# Something Special

---

# Introduction to USvideos

- Collected via Youtube API(Application Programming Interface)

- Consists of 4998 rows, 13 variables

- Videos collected from June 17th, 2008 to December 8th, 2017

- Videos posted within the United States

---

# Variables Used

- title, Name of the Youtube video

- category_id, Which category does the video fall under

- publish_time, What time of day did the video release 

- views, How many views did the video receive

- likes, How many likes did the video receive

- comment_count, How many comments did the video receive

---
class: inverse, middle, center

# Using xaringan

---

# xaringan

- The presentation is created using the `xaringan` package

- Use `---` to separate slides and `--` for incremental builds

--

- Like this

---

# Layouts

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
[*] And add footnotes
]

---

class: inverse, middle, center

# Data Visualization

---

# Data Cleaning

- We had duplicate Youtube videos in separate rows so we merged the duplicate rows into one single row and also combined the views, likes and comments together.

- This allows for us to rank the with accuracy because it adds up the total of the duplicate rows and gives us total values. 
```{r cleaned, echo = FALSE}
USvideos = USvideos[order(USvideos[,'title'],- USvideos[,'views']),] 
  USvideos = USvideos[!duplicated(USvideos$title),]
```


---

# Most Viewed


```{r filtering, echo = FALSE}
USvideos %>% 
  group_by(title, views) %>% 
  arrange(desc(views)) %>%
  distinct(title, views)  %>%
  print(tbl_USvideos(USvideos), n = 100)
```



---

## During what times of day do Youtubers post?


```{r capital-letters, echo = FALSE}

```

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger

```
]

---

# Time of Day 

- The different times of day used in previous slide is presented in military time or the 24-hour clock and it is defined below: 

- Morning: 06:00:00 ~ 11:59:59

- Afternoon: 12:00:00 ~ 17:59:59

- Evening: 18:00:00 ~ 23:59:59

- Midnight: 00:00:00 ~ 05:59:59


.footnote[
[*] The time intervals defined was recorded in Eastern Standard Time (GMT -5)
]
---

# Question/Exclamation mark effects on popularity

- Is "clickbait" real? Does it affect the amount of traffic a video receives or is it just a theory. Are "clickbait" videos more prone to dislikes because of a misleading title?

```{r question-or-exclamation, echo=FALSE}
USvideos %>% 
  filter_all(any_vars(str_detect(str_to_lower(.), "\\?|\\!"))) %>%
  select(title, views, likes, dislikes, comment_count) %>%
  arrange(desc(views))
```

---


# What is the most popular category?

- If people wanted to become famous overnight, what category type will increase their chances of being famous. 
```{r popular-categories, echo=FALSE}
USvideos %>% 
  filter_all(any_vars(str_detect(str_to_lower(.), "\\?|\\!"))) %>%
  select(title, views, likes, comment_count) %>%
  arrange(desc(views))
```

---

# Insert the most popular video thumbnail and maybe include the comments

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Statistical Inferences 

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# End

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what 
I expect majority of you will do. You will differentiate yourself with the content 
of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer/. 
